---
title: 'Blockchain on Twitter: A Sword of Damocles?'
author: "Shan Shan"
date: "12/18/2017"
output:
  html_document: default
  pdf_document: default
---


### Blockchain is the world's leading software platform for digital assets. Google Trends shows that Blockchain has a boost in the year 2017. What is Twitterers attitudes toward blockchain? My project analyzes Twitter data with the keyword blockchain from 2017 01 01 to 2017 12 18. To explore the brand perception of blockchain on Twitter, I have conducted word frequency analysis, sentiment analysis, and mapping analysis.




```{r}
#Set up Twitter

library(reshape)
library(reshape2)
library(devtools)
library(twitteR)
library(tm)
library(stringr)
library(wordcloud)
library(tidytext)
library(tidyverse)
library(streamR)
library(ROAuth)
library(reshape)
library(dplyr)
library(ggplot2)
library(plotly)
library(grid) 
library(lubridate)
library(graphTweets)
library(igraph)
library(streamR)
```


#### I. Read Twitter Data 

> * 1.1 Connect to Twitter API

```{r}
api_key <- "Y9sY5tXFzxNGvUJYd1Um0Z1Ux"
api_secret <- "HHnbEWbyLLuSqg3tvjPhYfl5HWQnzh2Jxxqo1ZbmVv8FgPrJWW"
access_token <- "817556180717412352-nPKehdlSsJ0pdRzFI25uhzowIBMKqR7"
access_token_secret <- "bWyPN9Xsi3kSmhlKlk0ls9cDosDcleYMpSSjkH7Q7WnHF"
  
setup_twitter_oauth(api_key, api_secret, access_token, access_token_secret)

```


>* 1.2 Read data

```{r}
blch <- searchTwitter('blockchain',since='2017-01-01', until='2017-12-18',lang = "en", n=1000) %>% twListToDF()
head(blch)

write.csv(blch, "blockchain.csv")
```

#### II.Word Frequency Blockchain -- Sword of Damocles? 

>* 2.1 Text Analysis of Top Words  (tokenize)

```{r, include=FALSE}
library(dplyr)
library(tidytext)

blch%>%
  unnest_tokens(word, text)

```

```{r}
tidy_blch<- blch%>% unnest_tokens(word,text)

tidy_blch%>%  count(word, sort=TRUE)


tidy_blch%>%
  count(word, sort = TRUE) %>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

>* 2.2 Sentiment Analysis
>  sentiment analysis of positive and negtive words
>  please refer to NRC Emotion Lexicon about the classification


```{r}
get_sentiments("afinn")

get_sentiments("bing")

get_sentiments("nrc")
```

```{r}

nrcpos <- get_sentiments("nrc") %>% 
  filter(sentiment == "positive")

tidy_blch%>%
  inner_join(nrcpos) %>%
  count(word, sort = TRUE)


nrcneg <- get_sentiments("nrc") %>% 
  filter(sentiment == "negative")

tidy_blch%>%
  inner_join(nrcneg) %>%
  count(word, sort = TRUE)

nrcfear <- get_sentiments("nrc") %>% 
  filter(sentiment == "fear")

tidy_blch%>%
  inner_join(nrcfear) %>%
  count(word, sort = TRUE)

nrcjoy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

tidy_blch%>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE)
```


```{r}


(fearlist <- tidy_blch%>%
  inner_join(nrcfear) %>%
  count(word, sort = TRUE))

(joylist <- tidy_blch%>%
  inner_join(nrcjoy) %>%
  count(word, sort = TRUE))

fearlist %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="blue") +
  xlab(NULL) +
  coord_flip() +
  scale_y_continuous(limits = c(0,60))

joylist %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="red") +
  xlab(NULL) +
  coord_flip() +
  scale_y_continuous(limits = c(0,60))
```

>* 2.3 Summary

>* From the Twitters, the word bonus are mentioned over 60 time, indicating it is an important sentiment of people towards blockchain.

> * The word improvement appeared over 30 times. This is also an important sentiment here. Some words like disaster, and caution may indicate something about people's worry. 


> * 2.4 Sentiment analysis with bing

```{r}
bingpos <- get_sentiments("bing") %>% 
  filter(sentiment == "positive")

(poslist <- tidy_blch%>%
  inner_join(bingpos) %>%
  count(word, sort = TRUE))


bingneg <- get_sentiments("bing") %>% 
  filter(sentiment == "negative")

(neglist <- (tidy_blch%>%
  inner_join(bingneg)  %>%
  count(word, sort = TRUE)))

poslist %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="red") +
  xlab(NULL) +
  coord_flip() +
  scale_y_continuous(limits = c(0,110))

neglist %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(fill="blue") +
  xlab(NULL) +
  coord_flip() +
  scale_y_continuous(limits = c(0,110))
```

> * 2.5. Summary 

>* From the Twitters, the word dark are mentioned is 61 times, indicating it is an impressive negative sentiment of people towards blockchain.

>* The word bonus appeared over 60 times. This is also an important sentiment here. 

>* Words like glad, and easier" may indicate something about people's expectaiton of blockchain. 

>* Therefore, it seems that people holds a half-and-half attitudes towards blockchain.

> * 2.6 Wordcloud

```{r}
library(wordcloud)


tidy_blch%>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```


```{r}
  tidy_blch %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("#F8766D", "#00BFC4"),
                   max.words = 100)
```



>* The cloud figure supports my former analysis that people holds a half-and-half attitudes towards blockchain.


#### IV. A “summit” day– Dec 17 2017

```{r}
# by date
(dates <- blch%>%
  mutate(date=date(created)) %>%
  group_by(date) %>%
  summarise(date_n = n()))

ggplot() +
  geom_bar(data=dates, 
           aes(date,date_n),
           stat = "identity", 
           fill="#f1801d") +
  ylab("Number of tweets") +
  scale_x_discrete(limits=lubridate::date(dates$date),labels=lubridate::date(dates$date))
```

>* The number of tweets about blockchain in December 17 are higher than other dates.

```{r}
# First 10 rows The tweets on dec 17

blch%>%
  filter(date(created)==c("2017-12-17")) %>%
  .$text %>%
  head(10)

blch%>%
  filter(date(created)==c("2017-12-17")) %>%
  nrow()

```

```{r}
# number of tweets containing blockchain on Dec 17
blch%>%
  filter(date(created)==c("2017-12-17")) %>%
  filter(grepl("blockchain",text)) %>%
  nrow

```

```{r}
# number of tweets containing develop on Dec 17
blch%>%
  filter(date(created)==c("2017-12-17")) %>%
  filter(grepl("improve",text)) %>%
  nrow

```

#### V. Where are the blockchain Twitterers? 

```{r}
load("my_oauth.Rdata")

filterStream("blockchainmap.json", 
             track=c("blockchain"), 
             locations = c(-125, 25, -66,50), 
             timeout=200, oauth=my_oauth)
blockchainmap<-parseTweets("blockchainmap.json", verbose = TRUE)
ck1 <- sum(blockchainmap$lat>0, na.rm = TRUE)
ck2 <- sum(blockchainmap$place_lat>0, na.rm = TRUE)
ck3 <- sum(!is.na(blockchainmap$location))
map.data <- map_data("state")   
netpoints <- data.frame(x = as.numeric(blockchainmap$lon),  
                       y = as.numeric(blockchainmap$lat))
netpoints <- netpoints[netpoints$y > 25, ]  
netpoints<-filter(netpoints,y>19&y<65,x>(-161.7)&x<(-68.01))
ggplot(map.data) + 
  geom_map(aes(map_id = region),  
           map = map.data,  
           fill = "white",             
           color = "grey20", size = 0.25) + 
  expand_limits(x = map.data$long, y = map.data$lat) +            
  theme(axis.line = element_blank(),  
        axis.text = element_blank(),  
        axis.ticks = element_blank(),                     
        axis.title = element_blank(),  
        panel.background = element_blank(),  
        panel.border = element_blank(),                     
        panel.grid.major = element_blank(), 
        plot.background = element_blank(),                     
        plot.margin = unit(0 * c( -1.5, -1.5, -1.5, -1.5), "lines")) +  
        geom_point(data = netpoints,             
        aes(x = x, y = y), size = 1,  
        alpha = 1/5, color = "red")  
```

>* The map displays that east part of U.S., such as New York; and the west part like California, have the most people twittering the blockchain topic


#### General Findings

> The sentiment analyses presents that some people regards blockchain as a improvement, while others regard it risky. 
> In the negative chart, the word dark is mentioned is 35 times
> In the positive chart, the positive word bonus is also mentioned around 35 times.   
> The cloud text visualized this half-half attitude balance as well                                   Therefore, we could assume that people holds a half-and-half attitudes towards blockchain
> The number of tweets about blockchain on December 17 reached the highest amount than other dates.
> The map displays that east part of U.S., such as New York; and the west part like California, have the most people twittering the blockchain topic

#### Links
SHINY APP
https://shshan.shinyapps.io/blockchain_on_twitter/

GIT HUB
https://github.com/shan-bu-2017/Twitterers-and-Blockchain.git




